Draft TLF generator

### 2023-04-27 posts/manipulate/draft_tlf_generator.qmd
Update draft_tlf_generator.qmd

@@

<details><summary  class = "block2"> <font color="blue"> demo_t_generator </font> __(click)__ </summary>

>>>>

Please find the code of this section in <font color="blue"> [add_model_name](https://posit.cloud/content/5870060) </font>

@@

<details><summary  class = "block2"> <font color="blue"> mock.yaml </font> __(click)__ </summary>
